Scalar and Representative Models for Polarimetric SAR Data

### 2013-05-18 paper_dev/article.tex
201305_May18 update from last version of 201305_May17

\begin{abstract}
This paper presents several novel scalar statistical models to represent the determinant of both partial and full polarimetric SAR (POLSAR) covariance matrices.
Compared to other scalar statistical models for POLSAR,
  the proposed models are highly representative of the multi-dimensional data
  and enable useful discrimination measures to be determined easily. %consequently they lead to useful discrimination measures.
When the multi-dimensional models are collapsed to a one-dimensional case,
  they are shown to exactly match the traditional statistical models for SAR intensity.
The paper validates the theoretical models together with their derived discrimination measures using real world POLSAR data.  
The proposed generic models are envisioned to enable the adaptation of many existing SAR data processing techniques for use with POLSAR data.
An  example is also shown where the determinant-ratio and its additive version, contrast, are applied in the evaluation of POLSAR speckle filters.
\end{abstract}

@@

While statistical models are important in understanding the stochastic nature of both SAR and POLSAR, in extending our understanding towards multi-dimensional POLSAR, an important issue needs to be addressed.
Namely that there now exists not one but many observables quantities in multi-channel POLSAR (as opposed to single-channel SAR intensity).
The research community has responded largely by developing different statistical models for various POLSAR observables.
However for a statistical model to be useful, scalar discrimination measures generally need to be derivable from it.
Thus, practical applications for POLSAR data processing require dis-similarity measures that are scalar, consistent and preferably homoskedastic on the one hand.
On the other hand, the observable quantity being modelled should be naturally representative of the high dimensionality POLSAR data.

This paper presents novel statistical models for multi-dimensional POLSAR data which generalize the commonly used statistical model for the one-dimensional SAR data and thus enables the adaptation of many existing SAR data processing techniques for POLSAR data.
Specifically statistical models for the heteroskedastic POLSAR determinant and its homoskedastic log-domian determinant, together with several other discrimination measures are derived in section  \ref{sec:theoretical_model}.
The representative properties of these observables are then demonstrated in section \ref{sec:sar_special_case_of_polsar}
  where the multi-dimensional POLSAR data is collapsed to a one-dimensional SAR scenario.
With this transformation, the determinant of the POLSAR covariance matrix is shown to be equivalent to SAR intensity,
  which also brings many standard statistical models used with SAR  under the umbrella of these generic POLAR models.
The proposed theoretical models are then validated against real life practical data in section \ref{sec:polsar_models_validation}.
Section \ref{sec:discussion} briefly describes how evaluation of an existing SAR data processing technique, the speckle filter, can be extended to  POLSAR data processing using this approach.
This is followed by a conclusion in Section \ref{sec:conclusion}.

@@

This section outlines related published work.
In particular, section \ref{sec:lit_models} reviews various scalar statistical models used for different POLSAR observables.
Its purpose is to show that none of those  models have led to statistically consistent discrimination measures. 
Section \ref{sec:lit_measures} further strengthen these findings by discussing discrimination measures that have been proposed for POLSAR,
  and demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
However, while an exact statistical distribution is needed for the test,
  only an symptotic distribution is used in the original work \cite{Conradsen_2003_TGRS_4}.

@@

Different target decomposition theorems have identified many different scalar observables for complex POLSAR data.
In \cite{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables is evaluated for classification purposes.
While many scalar observables for POLSAR were presented, their corresponding statistical models and classifiers were not available.
Furthermore, at its conclusion, the paper indicated that: it is impossible to identify the best representation.
To be fair, those observables were identified to describe a decomposed portion of the complex POLSAR data,
  rather than providing a single unified representation of the POLSAR data.

@@

The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined as:
\begin{align}
  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
\end{align}
where $A_{i,j}$ denotes the (i,j) elements of the matrix A,
 $||$ denotes absolute values
and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
However, in the context of POLSAR covariance matrix, these dis-similarity measures are not widely used 
  probably because of the multiplicative nature of the noisy data.

In the field of POLSAR, the Wishart distance is probably the most widely used as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
It is defined as \cite{Lee_1994_IJRS_2299}
\begin{equation}
  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
\end{equation}
As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.

Recent works have suggested a number of other dissimilarity measures.
These include the asymmetric and symmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
\begin{align}
  d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
    d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
\end{align}
the Bartlett distance \cite{Kersten_2005_TGRS_519},
  \begin{align}
  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
  \end{align}
the Bhattacharyya distance \cite{Lee_2011_IGARSS_3740},
\begin{equation}
  r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
\end{equation}
and the Wishart Statistical test distance \cite{Cao_2007_TGRS_3454}
\begin{equation}
  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
\end{equation}
.

@@

In this section, several scalar statistical models for POLSAR are presented.
After section \ref{sec:model_basic} briefly introduce the basic foundations, concepts and notation of this paper, %reviews related work in published literature,
  section \ref{sec:polsar_heterosked_model_and_log_transform}
  presents the theoretical models together with mathematical evidence for two related points.
The first point is that: the POLSAR data is multiplicative and heteroskedastic in its original domain.
And the second conclusion states: log-transformation converts it into an additive and homoskedastic model.
Several consistent measures of distance are then derived and presented in section \ref{sec:distance_measure}.

@@

The approach taken in this paper differs by applying the homoskedastic log transformation  on a less-than-well-known result for the determinant of the covariance matrix.
Goodman \cite{Goodman_1963_AMS_178} proved
that the ratio between the observable and expected values of the sample covariance matrix's determinants
  behaves like a product of $d$ chi-squared random variables with different degrees of freedom: 
\begin{equation}
\chi^d_L = (2L)^d \frac{|C_v|}{|\Sigma_v|} \sim \prod_{i=0}^{d-1} \chi^2 (2L-2i)
\label{eqn:prod_chi_squared_rv}  
\end{equation}

Its log-transformed variable consequently 
  behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom  
\begin{equation}
\Lambda^d_L = ln \left[ (2L)^d \frac{|C_v|}{|\Sigma_v|} \right] \sim \sum_{i=0}^{d-1} \Lambda^\chi (2L-2i)
\label{eqn:sum_log_chi_squared_rv}
\end{equation}
with
  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$

@@

For a real world captured image, while the parameters $d$ and $L$ do not change for the whole image,
  the underlying $\Sigma_v$ is expected to differ from one region to the next.
Thus over a heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ vary depending on the underlying signal $\Sigma_v$. 
In such context, Eqn. \ref{eqn:var_det_is_heteroskedastic} implies that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$, which indicates its heteroskedastic property.
At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} reveals that
  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$, exhibiting its homoskedastic nature.

@@

Similar to the way dispersion and contrast is defined in our previous work \cite{Le_2010_ACRS},
  this section introduces the consistent sense of distance from different perspectives.
Assuming, on the one hand, that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
random variables,
  ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
  are the observable according to the following definitions:
\begin{eqnarray}
  \mathbb{R} &=& \frac{|C_v|}{|\Sigma_v|} \label{eqn:determinant_ratio_observables}\\
  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
\end{eqnarray}

On the other hand, under a looser assumption %From another perspective
  where the POLSAR is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
  the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables are the observables defined as:
\begin{eqnarray}
  \mathbb{D} &=& \ln{|C_v|} - avg(\ln{|C_v|}) \label{eqn:dispersion_observable}\\
  \mathbb{C} &=& \ln(|C_{v1}|) - \ln(|C_{v2}|) \label{eqn:contrast_observable}
\end{eqnarray}

@@

Since each elementary component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
  it is natural that these variables also follow fixed distributions.
Moreover, they are independent of the underlying signal $\Sigma_v$.

\section{SAR as the one-dimensional case of multi-dimensional POLSAR}
\label{sec:sar_special_case_of_polsar}

The previous section  introduced  theoretical models for 3-dimensional, d=3 full polarimetric and 2-dimensional, d=2 partial polarimetry, cases.
This section will show that the model is equally  applicable to the 1-dimensional d=1 case,
  which is physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into 1-dimensional conventional SAR data.
Mathematically, the sample covariance matrix is reduced to the sample variance while the determinant is equivalent to  the scalar value.
As variance is equal to intensity for SAR data, our result is consistent with previous results for SAR intensity data.
Hence this derivation can be considered as cross-validation evidence for the proposed POLSAR models
  as well as reminding us that SAR is a special case of POLSAR.

@@

Upon setting $d=1$ into the above equations,
  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with the following two cases.
First is the following results obtained from our previous works on single-look SAR \cite{Le_2010_ACRS} , i.e. $d=L=1$,
\begin{align*}
  I &\sim \bar{I} \cdot pdf \left[ e^{-R} \right] \\
  \log_2{I} &\sim \log_2{\bar{I}} + pdf \left[ 2^xe^{-2^x}\ln2 \right] \\
  \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ e^{-x} \right]  \\
  \mathbb{L} &= \log_2{I} - \log_2{\bar{I}} \sim pdf \left[ 2^xe^{-2^x}\ln2 \right]\\
  \mathbb{D} &= \log_2{I} - avg(\log_2{I}) \sim pdf \left[ e^{-(2^xe^{-\gamma})} 2^xe^{-\gamma} \ln2 \right] \\
  \mathbb{C} &= \log_2{I_1} - \log_2{I_2} \sim pdf \left[ \frac{2^x}{(1+2^x)^2} \ln2 \right] \\
  \mathbb{A} &= avg(\mathbb{L}) = -\gamma / \ln{2} \\
  \mathbb{V} &= var(\mathbb{L}) = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
  \mathbb{E} &= mse(\mathbb{L}) = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
\end{align*}
The second is the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
  \begin{eqnarray}
I &\sim& pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(x-\bar{N})-Le^{x-\bar{N}}} \right]
  \end{eqnarray}
Furthermore, the following derivations for multi-look SAR data
   show that it can be considered 
    either as extensions of the corresponding single-look SAR results
    or as simple cases of the POLSAR results:
  \begin{align*}
    \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right]\\
    \mathbb{L} &= \ln{I} - \ln{\bar{I}} \sim pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
    \mathbb{D} &= \ln{I} - avg(\ln{I}) \sim pdf \left[ \frac{e^{L[x-\psi^0(L)]-e^{[x-\psi^0(L)]}}}{\Gamma(L)} \right] \\
    \mathbb{C} &= \ln{I_1} - \ln{I_2} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right] \\
    \mathbb{A} &= avg(\mathbb{L}) = \psi^0(L) - \ln{L} \\
    \mathbb{V} &= var(\mathbb{L}) = \psi^1(L) \\
    \mathbb{E} &= mse(\mathbb{L}) = \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
  \end{align*}

@@

This section aims to verify the theoretical models against practical data.
Since the previous section have shown that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
  which have been validated extensively, only a quick validation is needed for this case.

Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
In the experiment the intensity of a single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
The histograms for the log-distance and contrast is then plotted against the theoretical PDF given above.
 The plot is obtained with ENL set to the nominal number of 4, and  good visual match is apparent in the final results.

@@

After this quick validation, the rest of this section focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
Specifically, section \ref{sec:valid_nominal_enl} demonstrates a naive validation, where the nominal ENL is used for the model.
While the match appears to be reasonably good, it can be further improved.
Section \ref{sec:improve_the_match_bw_theory_practice} discusses why the nominal look-number given by (POL)SAR processors may not be accurate,
  while section \ref{sec:valid_enl_estimation} proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in a homoskedastic model.
With the newly estimated ENL, section \ref{sec:valid_improve_practice} demonstrates that the match between the theoretical model and the practical data is indeed further improved.

@@

In summary the dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
  if the underlying parameters can be estimated reasonably well for the given image.   
However as described above a single ``true signal'' $|\Sigma_v|$ can have two different estimated values,
  depending on which estimation method was being used.
The discrepancy between these two values suggests that at least one parameter for the models was inaccurately estimated.
This is discussed in the next section.

@@

Even though the assumptions made in developing this theory have intentionally been kept minimal, 
  like all other similar models, the proposed model in this paper is built upon certain presumptions.
However, practical conditions may not always satisfy these prerequisites.
In this section, a common and observable gap between the conditions found in practical real-life data and the theoretical assumptions is discussed.

The assumption of statistical independence between samples (for both SAR and POLSAR data) is reasonable given that 
  the transmission and receipt of analogue signals independent for each radar pulse, i.e. for each resolution cell.
However, the actual imaging mechanism in a real-life (POL)SAR processor is that of a digital nature,
  where the analogue signal is fed into an analogue-to-digital (ADC) sampling and conversion process.  
Theoretically it is possible to define a sampling rate so that each digital pixel corresponds exactly to an separate analogue physical cell.
Practically however, to ensure ``perfect reconstruction'', the sampling rate is normally set at a slightly higher value than the Nyquist rate.

>>>>

\begin{abstract}
This paper presents several novel scalar statistical models to represent the determinant of both partial and full polarimetric SAR (POLSAR) covariance matrices.
Compared to other scalar statistical models for POLSAR,
  the proposed models are highly representative of the multi-dimensional data
  and enable useful discrimination measures to be easily determined. %consequently they lead to useful discrimination measures.
When the multi-dimensional models are collapsed to a single dimension,
  they are shown to exactly match the traditional statistical models for SAR intensity.
The paper validates the theoretical models together with their derived discrimination measures using real world POLSAR data.  
%IVMThe proposed generic models are envisioned to enable the adaptation of many existing SAR data processing techniques for use with POLSAR data.
The intention is that these proposed generic models can facilitate the adaptation of existing SAR techniques to higher-dimensional POLSAR data.
To illstrate, an example is given where the determinant-ratio and its additive version, contrast, are applied in the evaluation of POLSAR speckle filters.
\end{abstract}

@@

While statistical models are important in understanding the stochastic nature of both SAR and POLSAR, in extending our understanding towards multi-dimensional POLSAR, an important issue needs to be addressed.
Namely that there now exists not one but many observable quantities in multi-channel POLSAR (as opposed to single-channel SAR intensity).
The research community has responded largely by developing different statistical models for various POLSAR observables.
However for a statistical model to be useful, scalar discrimination measures generally need to be derivable from it.
Thus, practical applications for POLSAR data processing require dis-similarity measures that are scalar, consistent and preferably homoskedastic on the one hand.
On the other hand, the observable quantity being modelled should be naturally representative of the high dimensionality POLSAR data.

This paper presents novel statistical models for multi-dimensional POLSAR data as generalisations of the commonly used one-dimensional SAR statistical model.
This approach makes feasible the adaptation of many existing SAR processing techniques, to be applied to POLSAR data.
Specifically, statistical models for the heteroskedastic POLSAR determinant and its homoskedastic log-domain equivalent, together with several other discrimination measures are derived in section  \ref{sec:theoretical_model}.
The representative properties of these observables are then demonstrated in section \ref{sec:sar_special_case_of_polsar}
  where the multi-dimensional POLSAR data is collapsed to a one-dimensional SAR scenario.
With this transformation, the determinant of the POLSAR covariance matrix is shown to be equivalent to SAR intensity,
  which also brings many standard statistical models used with SAR  under the umbrella of these generic POLAR models.
The proposed theoretical models are then validated against real life practical data in section \ref{sec:polsar_models_validation}.
Section \ref{sec:discussion} briefly describes how evaluation of an existing SAR data processing technique, the speckle filter, can be extended to  POLSAR data processing using this approach.
This is followed by a conclusion in Section \ref{sec:conclusion}.

@@

This section outlines related published work.
In particular, section \ref{sec:lit_models} reviews various scalar statistical models used for different POLSAR observables.
Its purpose is to show that none of those  models have led to statistically consistent discrimination measures. 
Section \ref{sec:lit_measures} further strengthens those findings by discussing discrimination measures that have been proposed for POLSAR,
  and demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
However, while an exact statistical distribution is needed for the test,
  only an symptotic distribution is used in the original work \cite{Conradsen_2003_TGRS_4}.

@@

Different target decomposition theorems have identified many possible scalar observables for complex POLSAR data.
In \cite{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables is evaluated for classification purposes.
While many scalar observables for POLSAR were presented, their corresponding statistical models and classifiers were not available.
Furthermore, at its conclusion, the paper indicated that it is impossible to identify a single best representation.
Although, to be fair, those observables were identified to describe a decomposed portion of the complex POLSAR data,
  rather than providing a single unified representation of the POLSAR data.

@@

The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined as:
\begin{align}
  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
\end{align}
where $C_{i,j}$ denotes the (i,j) elements of the matrix C,
 $||$ denotes absolute values
and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
However, in the context of POLSAR% covariance matrix
, these dis-similarity measures are not widely used 
  probably because of the multiplicative nature of the noisy data.

In the field of POLSAR, the Wishart distance is probably the most widely used, as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
It is defined \cite{Lee_1994_IJRS_2299} as:
\begin{equation}
  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
\end{equation}
As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.

Recent works have suggested alternative dissimilarity measures including the asymmetric and symmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
\begin{align}
  d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
    d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
\end{align}
the Bartlett distance \cite{Kersten_2005_TGRS_519},
  \begin{align}
  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
  \end{align}
the Bhattacharyya distance \cite{Lee_2011_IGARSS_3740},
\begin{equation}
  r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
\end{equation}
and the Wishart Statistical test distance \cite{Cao_2007_TGRS_3454}
\begin{equation}
  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
\end{equation}
.

%%***IVM: Hai, you haven't introduced the notation for these!! What is tr() (in eqn. 3), what is Lx, Ly.... I changed your A_{i,j} to C_{i,j} above, just after eqn.2

@@

In this section, several scalar statistical models for POLSAR are presented.
After section \ref{sec:model_basic} briefly introduces the basic foundations, concepts and notation of this paper, %reviews related work in published literature,
  section \ref{sec:polsar_heterosked_model_and_log_transform}
  presents the theoretical models together with mathematical evidence for two related points.
The first point is that the POLSAR data is multiplicative and heteroskedastic in its original domain.
And the second conclusion states that log-transformation converts it into an additive and homoskedastic model.
Some consistent measures of distance are then derived and presented in section \ref{sec:distance_measure}.

@@

The approach taken in this paper differs by applying the homoskedastic log transformation  on a less-than-well-known result for the determinant of the covariance matrix.
Goodman \cite{Goodman_1963_AMS_178} proved
that the ratio between the observable and expected values of the sample covariance matrix determinants
  behave like a product of $d$ chi-squared random variables with different degrees of freedom: 
\begin{equation}
\chi^d_L = (2L)^d \frac{|C_v|}{|\Sigma_v|} \sim \prod_{i=0}^{d-1} \chi^2 (2L-2i)
\label{eqn:prod_chi_squared_rv}  
\end{equation}

Its log-transformed variable consequently 
  behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom  
\begin{equation}
\Lambda^d_L = ln \left[ (2L)^d \frac{|C_v|}{|\Sigma_v|} \right] \sim \sum_{i=0}^{d-1} \Lambda^\chi (2L-2i)
\label{eqn:sum_log_chi_squared_rv}
\end{equation}
with
  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$.
We will now use this result to develop the statistical models for POLSAR. %log-transformed measures of distance.
%***IVM added the sentence above... **Please check it's true!!!!

@@

For a real world captured image, while the parameters $d$ and $L$ do not change for the whole image,
  the underlying $\Sigma_v$ is expected to differ from one region to the next.
Thus over a heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ vary depending on the underlying signal $\Sigma_v$. 
In such context, Eqn. \ref{eqn:var_det_is_heteroskedastic} implies that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$ (i.e. it is   heteroskedastic).
At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} reveals that
  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$ (i.e. it is homoskedastic).

@@

Similar to the way dispersion and contrast is defined for one-dimensional SAR \cite{Le_2010_ACRS},
  this section introduces the consistent sense of distance for POLSAR.
Assuming, on the one hand, that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
random variables,
  ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
  are observable according to the following definitions:
%Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv} lead straight to the definition of the following random variables, which is the :
\begin{eqnarray}
  \mathbb{R} &=& \frac{|C_v|}{|\Sigma_v|} \label{eqn:determinant_ratio_observables}\\
  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
\end{eqnarray}

On the other hand, under a looser assumption %From another perspective
  where the POLSAR data is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
  the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables are the observables defined as:
\begin{eqnarray}
  \mathbb{D} &=& \ln{|C_v|} - avg(\ln{|C_v|}) \label{eqn:dispersion_observable}\\
  \mathbb{C} &=& \ln(|C_{v1}|) - \ln(|C_{v2}|) \label{eqn:contrast_observable}
\end{eqnarray}

@@

Since each elementary component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
  it is natural that these variables also follow fixed distributions.
Moreover, note that they are independent of the underlying signal $\Sigma_v$.
%This result shows how
%In short, these random variables are shown to follow consistent and fixed distributions,
%  regardless of the underlying signal $\Sigma_v$.

\section{SAR as a one-dimensional case of POLSAR}
\label{sec:sar_special_case_of_polsar}

The previous section  introduced  theoretical models for 3-dimensional, d=3 full polarimetric and 2-dimensional, d=2 partial polarimetry, cases.
This section will show that the model is equally  applicable to the 1-dimensional d=1 case,
  which is physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into conventional single dimensional SAR data.
Mathematically, the sample covariance matrix is reduced to the sample variance while the determinant is equivalent to  the scalar value.
As variance is equal to intensity for SAR data, our result is consistent with previous results for SAR intensity data.
Hence this derivation can be considered as cross-validation evidence for the proposed POLSAR models
  as well as reminding us that SAR is a special case of POLSAR.

@@

Upon setting $d=1$ into the above equations,
  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with the following two cases.
First is the following results obtained from our previous work on single-look SAR \cite{Le_2010_ACRS} , i.e. $d=L=1$,
%Upon setting $d=1$ into the above models,
%  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
%not only the following results from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
\begin{align*}
  I &\sim \bar{I} \cdot pdf \left[ e^{-R} \right] \\
  \log_2{I} &\sim \log_2{\bar{I}} + pdf \left[ 2^xe^{-2^x}\ln2 \right] \\
  \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ e^{-x} \right]  \\
  \mathbb{L} &= \log_2{I} - \log_2{\bar{I}} \sim pdf \left[ 2^xe^{-2^x}\ln2 \right]\\
  \mathbb{D} &= \log_2{I} - avg(\log_2{I}) \sim pdf \left[ e^{-(2^xe^{-\gamma})} 2^xe^{-\gamma} \ln2 \right] \\
  \mathbb{C} &= \log_2{I_1} - \log_2{I_2} \sim pdf \left[ \frac{2^x}{(1+2^x)^2} \ln2 \right] \\
  \mathbb{A} &= avg(\mathbb{L}) = -\gamma / \ln{2} \\
  \mathbb{V} &= var(\mathbb{L}) = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
  \mathbb{E} &= mse(\mathbb{L}) = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
\end{align*}
The second is the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
  \begin{eqnarray}
I &\sim& pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(x-\bar{N})-Le^{x-\bar{N}}} \right]
  \end{eqnarray}
Furthermore, the following derivations for multi-look SAR data
   show that it can be considered 
    either as extensions of the corresponding single-look SAR results
    or as simple cases of the POLSAR results:
  \begin{align*}
    \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right]\\
    \mathbb{L} &= \ln{I} - \ln{\bar{I}} \sim pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
    \mathbb{D} &= \ln{I} - avg(\ln{I}) \sim pdf \left[ \frac{e^{L[x-\psi^0(L)]-e^{[x-\psi^0(L)]}}}{\Gamma(L)} \right] \\
    \mathbb{C} &= \ln{I_1} - \ln{I_2} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right] \\
    \mathbb{A} &= avg(\mathbb{L}) = \psi^0(L) - \ln{L} \\
    \mathbb{V} &= var(\mathbb{L}) = \psi^1(L) \\
    \mathbb{E} &= mse(\mathbb{L}) = \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
  \end{align*}

@@

This section aims to verify the theoretical models against practical data.
Since we have shown that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
  which have been validated extensively, only a simple validation is presented for this case.

Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
In the experiment, the intensity of single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
The histograms for the log-distance and contrast are then plotted against the theoretical PDF given above.
 The plot is obtained with ENL set to the nominal number of 4, and a good visual match is apparent, providing us a simple validation of the result.
%Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
%The ENL is set to the nominal number of 4.
%And good visual match is apparent in the final results.

@@

The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
Specifically, subsection \ref{sec:valid_nominal_enl} demonstrates a naive validation, where the nominal ENL is used for the model.
While the match appears to be reasonably good, it can be further improved.
Subsection \ref{sec:improve_the_match_bw_theory_practice} discusses why the nominal look-number given by (POL)SAR processors may not be accurate,
  while subsection \ref{sec:valid_enl_estimation} proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in a homoskedastic model.
With the newly estimated ENL, subsection \ref{sec:valid_improve_practice} demonstrates that the match between the theoretical model and the practical data is indeed further improved.

%Specifically the first sub-section provides a naive validation, where the nominal ENL is used for the model.
%While the match appears to be reasonably good, it can be further improved.
%After the second sub-section discusses why the nominal look-number given by (POL)SAR processors may not be very accurate,
%  the third sub-section proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in homoskedastic model.
%With the newly estimated ENL, the final sub-section shows that the match between the theoretical model and the practical data is indeed further improved.

@@

In summary the dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
  if the underlying parameters can be estimated reasonably well for the given image.   
However as described above a single ``true signal'' $|\Sigma_v|$ can have two different estimated values,
  depending on which estimation method was being used.
The discrepancy between these two values suggests that at least one parameter for the models was inaccurately estimated.
This is discussed in the next subsection.
%The discrepancy suggests that at least one parameter for the models was inaccurately estimated.
%In fact, the next sub-section specifically indicates that the nominal look-number given by the (POL)SAR processor may not accurately reflect the true nature of the captured data.

%But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
%The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
%  where not only the look number is shown to be misused
%  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
%As will be shown in Section \ref{sec:improve_the_match_bw_theory_practice}, 
%  the reason is due to the inappropriate look number being used.
%Furthermore, the match between the theoretical model and the practical data will also be shown to improve once a more accurate look number (ENL) is estimated.  
%For now, let us simply observe that
%  using appropriate estimation of the parameters, 
%  the proposed models match reasonably well with the practical data.

@@

Even though the assumptions made in developing this theory have intentionally been kept minimal, 
in common with other similar derivations the proposed model in this paper is built upon certain presumptions.
However, practical conditions may not always satisfy these prerequisites, thus we find a common and observable gap between the conditions found in practical real-life data and the theoretical assumptions.

The assumption of statistical independence between samples (for both SAR and POLSAR data) is reasonable given that 
  the transmission and receipt of analogue signals is independent for each radar pulse, i.e. for each resolution cell.
However, the actual imaging mechanism in a real-life (POL)SAR processor is of a digital nature,
  where the analogue signal is fed into an analogue-to-digital (ADC) sampling and conversion process.  
Theoretically it is possible to define a sampling rate so that each digital pixel corresponds exactly to an separate analogue physical cell.
Practically however, to ensure ``perfect reconstruction'', the sampling rate is normally set at a slightly higher value than the Nyquist rate.
